Model_CFU

### 2017-01-09 code/HumanCdGF_cdiff_colonization.Rmd

randomized_cfu_src_df <- c()
randomized_src_rsq <- c()
for(i in 1:100){
  set.seed(i)
  random_cfu <- sample(cfu_all_src_shared_df$log_cfu_med, 
                       length(cfu_all_src_shared_df$log_cfu_med), replace = F)
  set.seed(seed)
  randomized_cfu_src_rf <- randomForest(cfu_all_src_shared_df[ , -1], random_cfu,
                           ntree = 501,
                           mtry = 15)
  randomized_cfu_src_df <- rbind(randomized_cfu_src_df, 
                               data.frame(Model = 'Randomized', Observed = random_cfu,
                                          Predicted = randomized_cfu_src_rf$predicted))
  randomized_src_rsq <- c(randomized_src_rsq, tail(randomized_cfu_src_rf$rsq,1))

@@

randomized_wo581 <- c()
base_wo581_rsq <- c()
for(i in 1:100){
  set.seed(i)
  random_cfu <- sample(cfu_wo581_df$log_cfu_med, 
                       length(cfu_wo581_df$log_cfu_med), replace = F)
  set.seed(seed)
  randomized_wo581_rf <- randomForest(cfu_wo581_df[ , -1], random_cfu,
                           ntree = 501,
                           mtry = 15)
  randomized_wo581 <- rbind(randomized_wo581, 
                               data.frame(Model = 'Randomized', Observed = random_cfu,
                                          Predicted = randomized_wo581_rf$predicted))
  base_wo581_rsq <- c(base_wo581_rsq, tail(randomized_wo581_rf$rsq,1))
}
set.seed(seed)
cfu_wo581_rf <- randomForest(cfu_wo581_df[ , -2], cfu_wo581_df$log_cfu_med,
                           ntree = 1001,
                           mtry = 15,
                           importance = T)
top_features_wo581 <- head(sort(importance(cfu_wo581_rf)[,1],decreasing = T), n_features)

@@

randomized_wo_hilo <- c()
base_wo_hilo_rsq <- c()
for(i in 1:100){
  set.seed(i)
  random_cfu <- sample(cfu_wo_hilo_df$log_cfu_med, 
                       length(cfu_wo_hilo_df$log_cfu_med), replace = F)
  set.seed(seed)
  randomized_wo_hilo_rf <- randomForest(cfu_wo_hilo_df[ , -1], random_cfu,
                           ntree = 501,
                           mtry = 15)
  randomized_wo_hilo <- rbind(randomized_wo_hilo, 
                               data.frame(Model = 'Randomized', Observed = random_cfu,
                                          Predicted = randomized_wo_hilo_rf$predicted))
  base_wo_hilo_rsq <- c(base_wo_hilo_rsq, tail(randomized_wo_hilo_rf$rsq,1))
}
set.seed(seed)
cfu_wo_hilo_rf <- randomForest(cfu_wo_hilo_df[ , -2], cfu_wo_hilo_df$log_cfu_med,
                           ntree = 1001,
                           mtry = 15,
                           importance = T)
top_features_wo_hilo <- head(sort(importance(cfu_wo_hilo_rf)[,1],decreasing = T), n_features)

>>>>

randomized_cfu_src_df <- c()
randomized_src_rsq <- c()
for(i in 1:100){
  set.seed(i)
  random_cfu <- sample(cfu_all_src_shared_df$log_cfu_med, 
                       length(cfu_all_src_shared_df$log_cfu_med), replace = F)
  set.seed(seed)
  randomized_cfu_src_rf <- randomForest(cfu_all_src_shared_df[ , -c(1,2)], random_cfu,
                           ntree = 501,
                           mtry = 15)
  randomized_cfu_src_df <- rbind(randomized_cfu_src_df, 
                               data.frame(Model = 'Randomized', Observed = random_cfu,
                                          Predicted = randomized_cfu_src_rf$predicted))
  randomized_src_rsq <- c(randomized_src_rsq, tail(randomized_cfu_src_rf$rsq,1))

@@

randomized_wo581 <- c()
base_wo581_rsq <- c()
for(i in 1:100){
  set.seed(i)
  random_cfu <- sample(cfu_wo581_df$log_cfu_med, 
                       length(cfu_wo581_df$log_cfu_med), replace = F)
  set.seed(seed)
  randomized_wo581_rf <- randomForest(cfu_wo581_df[ , -c(1,2)], random_cfu,
                           ntree = 501,
                           mtry = 15)
  randomized_wo581 <- rbind(randomized_wo581, 
                               data.frame(Model = 'Randomized', Observed = random_cfu,
                                          Predicted = randomized_wo581_rf$predicted))
  base_wo581_rsq <- c(base_wo581_rsq, tail(randomized_wo581_rf$rsq,1))
}
set.seed(seed)
cfu_wo581_rf <- randomForest(cfu_wo581_df[ , -2], cfu_wo581_df$log_cfu_med,
                           ntree = 1001,
                           mtry = 15,
                           importance = T)
top_features_wo581 <- head(sort(importance(cfu_wo581_rf)[,1],decreasing = T), n_features)

@@

randomized_wo_hilo <- c()
base_wo_hilo_rsq <- c()
for(i in 1:100){
  set.seed(i)
  random_cfu <- sample(cfu_wo_hilo_df$log_cfu_med, 
                       length(cfu_wo_hilo_df$log_cfu_med), replace = F)
  set.seed(seed)
  randomized_wo_hilo_rf <- randomForest(cfu_wo_hilo_df[ , -c(1,2)], random_cfu,
                           ntree = 501,
                           mtry = 15)
  randomized_wo_hilo <- rbind(randomized_wo_hilo, 
                               data.frame(Model = 'Randomized', Observed = random_cfu,
                                          Predicted = randomized_wo_hilo_rf$predicted))
  base_wo_hilo_rsq <- c(base_wo_hilo_rsq, tail(randomized_wo_hilo_rf$rsq,1))
}
set.seed(seed)
cfu_wo_hilo_rf <- randomForest(cfu_wo_hilo_df[ , -2], cfu_wo_hilo_df$log_cfu_med,
                           ntree = 1001,
                           mtry = 15,
                           importance = T)
top_features_wo_hilo <- head(sort(importance(cfu_wo_hilo_rf)[,1],decreasing = T), n_features)
